Associative Data Structures for Website Filtering

### 2014-04-17 paper/paper.tex
wrote the abstract, added quotues to the research questions

    How does the number of entries influence the performance of various associative data structures?

@@

    How does the complexity of the key influence the preformance of various associative data structures?

>>>>

    \begin{quotation}How does the number of entries influence the performance of various associative data structures?\end{quotation}

@@

    \begin{quotation}How does the complexity of the key influence the preformance of various associative data structures?\end{quotation}
